---
title: "Fin_bodywt"
format: html
editor: visual
---

## MST-66

Experiment on 20 CBA/J mice. Daily weights.

Finerenone started at 10 mg/kg daily by oral gavage on 4/16/2026,

S typh infection by oral gavage on 4/23/2026.

```{r}
library(tidyverse)
library(readxl)
library(janitor)
library(ggtext)
```

### Import data file

```{r}
dt <- readxl::read_excel("MST-66_bodywt.xlsx")
```

Now let's make the basic plot

Questions:

1.  Does finerenone make inflammation worse, cause mortality with intestinal inflammation (like spironolactone?)
2.  Does finerenone reduce intestinal fibrosis- like it does in heart and kidney?

```{r}
dt |> 
  pivot_longer(cols = -c(Tx:cage),
               names_to = 'date',
               values_to = 'weight_g') |> mutate(date = excel_numeric_to_date(as.numeric(date))) |> 
  ggplot() +
  aes(x = date, y = weight_g, color = Tx, group = Tx) +
  geom_jitter(width = 0.4) +
  geom_smooth() +
  labs(x = 'Date', y = "Mouse Body Weight (g)", title = "<span style='color:blue;'>Finerenone</span> Prevention in the *Salmonella typhimurium*<br>Inflammation-to-Fibrosis Mouse Model") +
  annotate(geom = 'text', x = as.Date("2026-04-15"), y = 23.5, label = "Finerenone", color = "blue") +
  annotate(geom = 'text', x = as.Date("2026-04-15"), y = 19.5, label = "Control", color = 'red') +
  annotate(geom = 'richtext', x = as.Date("2026-04-16"), y = 17.4, label = "Start <span style='color:blue;'>Finerenone</span><br>on 16 April") + geom_segment(aes(x = as.Date("2026-04-16"),  xend  = as.Date("2026-04-16"), y = 17, yend = 15), color = 'black',
  arrow = arrow(length = unit(0.2, "cm"))) +
  annotate(geom = 'richtext', x = as.Date("2026-04-23"), y = 16.4, label = "Start *Salmonella*<br>infxn on 23 April") +
   geom_segment(aes(x = as.Date("2026-04-23"),  xend  = as.Date("2026-04-23"), y = 16, yend = 15), color = 'black',
  arrow = arrow(length = unit(0.2, "cm"))) +
  geom_segment(aes(x = as.Date("2026-04-23"),  xend  = as.Date("2026-04-23"), y = 16.8, yend = 19), color = 'black',
  arrow = arrow(length = unit(0.2, "cm"))) +
  scale_color_manual(values = c('blue', 'red')) +
  theme_linedraw()+
  theme(legend.position = 'none') +
   theme(
    plot.title = element_markdown() # Required to render the HTML/Markdown
  )

```

Try without smoothing - averaging and curves

```{r}
dt |> 
  pivot_longer(cols = -c(Tx:cage),
               names_to = 'date',
               values_to = 'weight_g') |> mutate(date = excel_numeric_to_date(as.numeric(date))) |> 
  ggplot() +
  aes(x = date, y = weight_g, color = Tx, group = Tx) +
  geom_jitter(width = 0.3) +
  stat_summary(fun = "mean", geom = "line", aes(group = Tx)) +
  labs(x = 'Date', y = "Mouse Body Weight (g)", title = "<span style='color:blue;'>Finerenone</span> Prevention in the *Salmonella typhimurium*<br>Inflammation to Fibrosis Mouse Model") +
  annotate(geom = 'text', x = as.Date("2026-04-15"), y = 23.2, label = "Finerenone", color = "blue") +
  annotate(geom = 'text', x = as.Date("2026-04-15"), y = 19.2, label = "Salmonella\nControl", color = 'red') +
  annotate(geom = 'text', x = as.Date("2026-04-16"), y = 17.5, label = "Start Finerenone\non 16 April") + geom_segment(aes(x = as.Date("2026-04-16"),  xend  = as.Date("2026-04-16"), y = 17, yend = 15), color = 'black',
  arrow = arrow(length = unit(0.2, "cm"))) +
  annotate(geom = 'text', x = as.Date("2026-04-23"), y = 16.5, label = "Start Salmonella\n infxn on 23 April") +
   geom_segment(aes(x = as.Date("2026-04-23"),  xend  = as.Date("2026-04-23"), y = 16, yend = 15), color = 'black',
  arrow = arrow(length = unit(0.2, "cm"))) +
  geom_segment(aes(x = as.Date("2026-04-23"),  xend  = as.Date("2026-04-23"), y = 17, yend = 19), color = 'black',
  arrow = arrow(length = unit(0.2, "cm"))) +
  scale_color_manual(values = c('blue', 'red')) +
  theme_linedraw()+
  theme(legend.position = 'none') +
   theme(
    plot.title = element_markdown() )
```
